---
title       : Predictive Text App Project
subtitle    : Natural Language Processing with Coursera and Swiftkey
author      : Lovelli Ariesti           
job         : Data Scientist
framework   : revealjs
transition  : cube
highlighter : highlight.js  
hitheme     : tomorrow    
widgets     : [mathjax]     
mode        : standalone 
knit        : slidify::knit2slides
---

# Close-Format-Nemesis
## A PREDICTIVE TEXT APP

###### created by [Lovelli Ariesti](https://github.com/ariesti)

--- .class1 #id1

## A Simple Plan

```{r img, echo=FALSE, fig.align='center'}
library(png)
library(grid)
img <- readPNG("C:/Users/Hp/Documents/DATA/Close-Format/assets/img/plot_dtm1.png")
grid.raster(img)
```

sample corpus plot

--- .class3 #1d3

Choose a time series:

```{r}
paste("Hello", "World!")
```

See a plot:

```{r eval=TRUE, echo = FALSE}
paste("Hello", "World!")
```

--- .class4 #id4

### Natural Language Processing

"Natural Language Processing applies machine learning algorithm to generate a larger set of **features** from the input data. Prior to machine learning, language processing tasks involved direct hand coding applied to large sets of rules, or what is also known as **annotation**. These rules are now learned using general learning algorithms."


